Expert-In-The-Loop Causal Discovery: Iterative Model Refinement Using Expert Knowledge

### 2025-02-07 paper/figures_v2.tex
Updates

		\draw [red, ->, >=stealth, transform canvas={yshift=0em}] (rln) to (age);
		\draw [blue,->, >=stealth, transform canvas={yshift=-0.3em}] (rln) to (age);

		\draw [red, ->, >=stealth, transform canvas={xshift=0.15em}] (inc) to (age);
		\draw [blue,->, >=stealth, transform canvas={xshift=-0.15em}] (inc) to (age);
		\draw [red, ->, >=stealth, transform canvas={xshift=0.15em, yshift=0.15em}] (inc) to (edu);
		\draw [blue,->, >=stealth, transform canvas={xshift=-0.15em, yshift=-0.15em}] (inc) to (edu);

		\draw [red, ->, >=stealth, transform canvas={yshift=0.15em}] (occ) to (hrpw);
		\draw [blue,->, >=stealth, transform canvas={yshift=-0.15em}] (occ) to (hrpw);

@@

		\draw [blue,->, >=stealth] (rln) to[bend right=50] (hrpw);
		\draw [blue,->, >=stealth] (hrpw) to[bend right=25] (edu);

>>>>

		\draw [red, ->, >=stealth, transform canvas={yshift=0em}] (rln) to (age);
		\draw [blue,->, >=stealth, transform canvas={yshift=-0.3em, xshift=0.1em}] (rln) to (age);

		\draw [red, ->, >=stealth, transform canvas={xshift=0.15em}] (inc) to (age);
		\draw [blue,->, >=stealth, transform canvas={xshift=-0.15em}] (inc) to (age);
		\draw [red, ->, >=stealth, transform canvas={yshift=0.15em}] (inc) to (edu);
		\draw [blue,->, >=stealth, transform canvas={xshift=-0.15em, yshift=-0.15em}] (inc) to (edu);

		\draw [red, ->, >=stealth, transform canvas={yshift=0.15em}] (occ.-170) to (hrpw.15);
		\draw [blue,->, >=stealth, transform canvas={yshift=-0.15em, xshift=0.1em}] (occ.-170) to (hrpw.15);

@@

		\draw [blue,->, >=stealth] (rln) to[bend right=50] (hrpw);
		\draw [blue,->, >=stealth] (hrpw) to[bend right=30] (edu);

### 2025-02-07 paper/main.tex
Updates

\begin{figure}[t!]
    \begin{subfigure}{0.5 \textwidth}
	\centering
    	\includegraphics[page=1]{figures_v2.pdf}
    	\caption{}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
    	\includegraphics[page=2]{figures_v2.pdf}
    	\caption{}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
    	\includegraphics[page=3]{figures_v2.pdf}
    	\caption{}
    \end{subfigure}

@@

\subsubsection{Both $ X $ and $ Y $ are continuous}
When both $ X $ and $ Y $ are continuous, Pearson's correlation coefficient is
typically used. When $ \bm{Z} = \emptyset $, the correlation
coefficient is defined as:

@@

\paragraph{All $ X $, $ Y $, and $ \bm{Z} $ are discrete}

@@

\paragraph{$ X $ is ordinal, and $ Y $ and $ Z $  are continuous or ordinal}

>>>>

\begin{figure}[t!]
    \begin{subfigure}{0.5 \textwidth}
	\centering
    	\includegraphics[page=1]{figures_v2.pdf}
    	\caption{}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
	\centering
    	\includegraphics[page=2]{figures_v2.pdf}
    	\caption{}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
	\centering
    	\includegraphics[page=3]{figures_v2.pdf}
    	\caption{}
    \end{subfigure}

@@

\paragraph{Both $ X $ and $ Y $ are continuous: }
When both $ X $ and $ Y $ are continuous, Pearson's correlation coefficient is
typically used. When $ \bm{Z} = \emptyset $, the correlation
coefficient is defined as:

@@

\paragraph{All $ X $, $ Y $, and $ \bm{Z} $ are discrete: }

@@

\paragraph{$ X $ is ordinal, and $ Y $ and $ Z $  are continuous or ordinal: }
